---
title: "Lab12"
author: "Andrea Dame"
date: "11/16/2020"
output: html_document
---
```{r}
BiocManager::install("RCy3")
```
```{r}
library(RCy3)
cytoscapePing()
```
# My first Network
```{r}
nodes <- data.frame(id=c("node 0","node 1","node 2","node 3"),
           group=c("A","A","B","B"), # optional
           stringsAsFactors=FALSE)
edges <- data.frame(source=c("node 0","node 0","node 0","node 2"),
           target=c("node 1","node 2","node 3","node 3"),
           interaction=c("inhibits","interacts","activates","interacts"),  # optional
           weight=c(5,3,5,9), # optional
           stringsAsFactors=FALSE)

createNetworkFromDataFrames(nodes,edges)
```

```{r}
getwd()
```

##Basic Data Visualization Tutorial Graph

![Gal_Yeast_Example_Graph] (/Users/andreadame/anaconda3/Applications/EvoGenomics/genomics-course/Yeast_Example_Graph.png)

##Differentially Expressed Genes Network Analysis
![String Network - ovarian cancer -1.png] (/Users/andreadame/anaconda3/Applications/EvoGenomics/genomics-course/String Network - ovarian cancer -1.png)
