---
title: "Lab3"
author: "Andrea Dame"
date: "9/7/2020"
output: html_document
---

```{r}
library(tidyverse)
```


```{r}
surveys <- read.csv("data/portal_data_joined.csv")
```

```{r}
head(surveys)
```
```{r}
View(surveys)
```

```{r}
?read.csv
```

```{r}
str(surveys)
```

```{r}
nrow(surveys)
```
```{r}
ncol(surveys)
```
###Challenge
### What is the class of the object surveys? How many rows and how many columns are in this object? How many species have been recorded during these surveys?

### The class is 'data frame'. There are 34786 rows with 13 coloumns. This accounts for 48 different species. 

```{r}
surveys[1, 1] 
surveys[1, 6]
surveys[, 1]
surveys[1] 
surveys[1:3, 7] 
surveys[3, ] 
head_surveys <- surveys[1:6, ] 
```
```{r}
surveys[1:10]
```
```{r}
surveys[10:1]
```
###Challenge 
### 1. Create a data.frame (surveys_200) containing only the data in row 200 of the surveys dataset.

```{r}
surveys_200 <- surveys[200, ]
surveys_200
```
### 2. Notice how nrow() gave you the number of rows in a data.frame? Use that number to pull out just that last row in the data frame.Compare that with what you see as the last row using tail() to make sure it’s meeting expectations.Pull out that last row using nrow() instead of the row number. Create a new data frame (surveys_last) from that last row.

```{r}
n_rows <- nrow(surveys)
n_rows
surveys_last <- surveys[n_rows, ]
surveys_last
```
### 3. Use nrow() to extract the row that is in the middle of the data frame. Store the content of this row in an object named surveys_middle.

```{r}
surveys_middle <- surveys[n_rows / 2, ]
surveys_middle
```
### 4. Combine nrow() with the - notation above to reproduce the behavior of head(surveys), keeping just the first through 6th rows of the surveys dataset.

```{r}
surveys_head <- surveys[-(7:n_rows), ]
surveys_head
```

```{r}
sex <- factor(c("male", "female", "female", "male"))
levels(sex)
nlevels(sex)
sex # current order
#> [1] male   female female male  
#> Levels: female male
sex <- factor(sex, levels = c("male", "female"))
sex # after re-ordering
#> [1] male   female female male  
#> Levels: male female
```

```{r}
as.character(sex)
```

```{r}
year_fct <- factor(c(1990, 1983, 1977, 1998, 1990))
as.numeric(year_fct)               # Wrong! And there is no warning...
as.numeric(as.character(year_fct)) # Works...
as.numeric(levels(year_fct))[year_fct]    # The recommended way.
```

```{r}
## bar plot of the number of females and males captured during the experiment:
plot(as.factor(surveys$sex))
```

```{r}
as.character(sex)
```
```{r}
year_fct <- factor(c(1990, 1983, 1977, 1998, 1990))
as.numeric(year_fct)               # Wrong! And there is no warning...
as.numeric(as.character(year_fct)) # Works...
as.numeric(levels(year_fct))[year_fct]    # The recommended way.
```
```{r}
## bar plot of the number of females and males captured during the experiment:
plot(as.factor(surveys$sex))
```
```{r}
sex <- factor(surveys$sex)
head(sex)
#> [1] M M        
#> Levels:  F M
levels(sex)
#> [1] ""  "F" "M"
levels(sex)[1] <- "undetermined"
levels(sex)
#> [1] "undetermined" "F"            "M"
head(sex)
#> [1] M            M            undetermined undetermined undetermined
#> [6] undetermined
#> Levels: undetermined F M
```
###Challenge
### Rename “F” and “M” to “female” and “male” respectively. Now that we have renamed the factor level to “undetermined”, can you recreate the barplot such that “undetermined” is last (after “male”)?
```{r}
levels(sex)[2:3] <- c("female", "male")
sex <- factor(sex, levels = c("female", "male", "undetermined"))
plot(sex)
```
```{r}
## Compare the difference between our data read as `factor` vs `character`.
surveys <- read.csv("data/portal_data_joined.csv", stringsAsFactors = TRUE)
str(surveys)
surveys <- read.csv("data/portal_data_joined.csv", stringsAsFactors = FALSE)
str(surveys)
## Convert the column "plot_type" into a factor
surveys$plot_type <- factor(surveys$plot_type)
```
###Challenge
### 1. We have seen how data frames are created when using read.csv(), but they can also be created by hand with the data.frame() function. There are a few mistakes in this hand-crafted data.frame. Can you spot and fix them? Don’t hesitate to experiment!

###There are missing quotations around animal names, missing a comma in weight column, mix of factors and numerics in has_kangaroo (FALSE and 1). using stringsAsFactors = FALSE would have made character vectors instead of factors. Removing the quotes in temperature and northern_hemisphere and replacing 1 by TRUE in the has_kangaroo column would give what was probably intended.

```{r}
str(surveys)
```
```{r}
library("lubridate")
```
```{r}
my_date <- ymd("2015-01-01")
str(my_date)
```
```{r}
# sep indicates the character to use to separate each component
my_date <- ymd(paste("2015", "1", "1", sep = "-")) 
str(my_date)
```
```{r}
paste(surveys$year, surveys$month, surveys$day, sep = "-")
ymd(paste(surveys$year, surveys$month, surveys$day, sep = "-"))
surveys$date <- ymd(paste(surveys$year, surveys$month, surveys$day, sep = "-"))
str(surveys) # notice the new column, with 'date' as the class
```
```{r}
summary(surveys$date)
```
```{r}
missing_dates <- surveys[is.na(surveys$date), c("year", "month", "day")]

head(missing_dates)
```

