---
title: "Lab9"
author: "Andrea Dame"
date: "10/26/2020"
output: html_document
---

```{r}
library(stringr)
library(tidyverse)
```

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "an")
```
```{r}
str_view(x, ".a.")
```
```{r}
# To create the regular expression, we need \\
dot <- "\\."

# But the expression itself only contains one:
writeLines(dot)
```

```{r}
# And this tells R to look for an explicit .
x <- c("abc", "a.c", "bef")
str_view(x, "a\\.c")
```
```{r}
x <- "a\\b"
writeLines(x)
```
```{r}
str_view(x, "\\\\")
```

# 14.3.1 Exercises
# 1 Explain why each of these strings don’t match a \: "\", "\\", "\\\".

# 1. The backdash \ is used to esacpe special behavior to the next character in the string and in strings, so it's not just a literal "\". Two backdashes "\\" is used to create a regular expression as a string, which will then just escape the next charcter in string. Three backdashes "\\\" will resolve to a literal backslash in the regular expression, then escape the next character in the string. So in the regular expression, this will escape some escaped character.

# 2 How would you match the sequence "'\?

# 2. You would use str_view("\"'\\", "\"'\\\\", match = TRUE) 

# 3 What patterns will the regular expression \..\..\.. match? How would you represent it as a string?

# 3. The regular expression \..\..\.. will match patterns that have a dot followed by any character. It will repeat 3 times for each \..

#Anchors
# ^ to match the start of the string. $ to match the end of the string.

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "^b")
```
```{r}
str_view(x, "r$")
```
```{r}
x <- c("apple pie", "apple", "apple cake")
str_view(x, "apple")
str_view(x, "^apple cake$")
```
# 14.3.2.1 Exercises

#1 How would you match the literal string "$^$"?
```{r}
x <- c("apple pie", "$^$", "apple cake")
str_view(x, "^\\$\\^\\$$")
```
# 14.3.3 Character classes and alternatives
# There are a number of special patterns that match more than one character. You’ve already seen ., which matches any character apart from a newline. There are four other useful tools:

# \d : matches any digit. \s : matches any whitespace (e.g. space, tab, newline). [abc] : matches a, b, or c. [^abc] : matches anything except a, b, or c.
```{r}
# Look for a literal character that normally has special meaning in a regex
x <- c("abc", "a.c", "a*c", "a c")
str_view(x, "a[.]c")
```
```{r}
str_view(x, ".[*]c")
```

```{r}
str_view(x, "a[ ]")
```
```{r}
x <- c("cat", "rat")
str_view(x, "(c|r)at")
```
# 14.3.3.1 Exercises

# 1 Create regular expressions to find all words that: Start with a vowel. That only contain consonants. (Hint: thinking about matching “not”-vowels.) End with ed, but not with eed. End with ing or ise.
```{r}
str_subset(stringr::words, "^[aeiou]")
```

```{r}
str_subset(stringr::words, "[aeiou]", negate=TRUE)
```

```{r}
str_view(stringr::words, "[aeiou]", match=FALSE)
```

```{r}
str_subset(stringr::words, "[^e]ed$")
```

```{r}
str_subset(stringr::words, "i(ng|se)$")
```

# 14.3.4 Repetition
# The next step up in power involves controlling how many times a pattern matches: ?: 0 or 1 +: 1 or more *: 0 or more

```{r}
x <- "1888 is the longest year in Roman numerals: MDCCCLXXXVIII"
str_view(x, "CC?")
```
```{r}
str_view(x, "CC+")
```

```{r}
str_view(x, 'C[LX]+')
```

# You can also specify the number of matches precisely: {n}: exactly n {n,}: n or more {,m}: at most m {n,m}: between n and m
```{r}
str_view(x, "C{2}")
```

```{r}
str_view(x, "C{2,}")
```

```{r}
str_view(x, "C{2,}")
```

```{r}
str_view(x, 'C{2,3}?')
```

```{r}
str_view(x, 'C[LX]+?')
```
# 14.3.4.1 Exercises
# Describe the equivalents of ?, +, * in {m,n} form.

```{r}
x <- "there is the spider aaaahhhhh"
str_view(x, "aa?")
```
```{r}
str_view(x, "aa{0,1}")
```
```{r}
str_view(x, "aa+")
```

```{r}
str_view(x, "aa{1,}")
```
```{r}
str_view_all(x, "a[hh]+")
```

```{r}
str_view_all(x, "a[hh]{1,}")
```

```{r}
str_view_all(x, "a[hh]*")
```
```{r}
str_view_all(x, "a[hh]{0,}")
```

#14.3.5 Grouping and backreferences
```{r}
str_view(fruit, "(..)\\1", match = TRUE)
```
# 14.3.5.1 Exercises
#Describe, in words, what these expressions will match: (.)\1\1 "(.)(.)\\2\\1" (..)\1 "(.).\\1.\\1" "(.)(.)(.).*\\3\\2\\1"

# (.)\1\1 will match to characters three in a row.  "(.)(.)\\2\\1"will match palindrome-like characters like anna or noon. (..)\1 will match repeating characters. "(.).\\1.\\1" will match  a character followed by any character, the original character, any other character, the original character again. "(.)(.)(.).*\\3\\2\\1" will match with anything that starts and ends with the same 3 characters but in reverse order at the end. 

# 14.4 Tools  
#Determine which strings match a pattern. Find the positions of matches. Extract the content of matches. Replace matches with new values. Split a string based on a match. 

# 14.4.1 Detect matches
```{r}
x <- c("apple", "banana", "pear")
str_detect(x, "e")
```

```{r}
# How many common words start with t?
sum(str_detect(words, "^t"))
```

```{r}
# What proportion of common words end with a vowel?
mean(str_detect(words, "[aeiou]$"))
```

```{r}
# Find all words containing at least one vowel, and negate
no_vowels_1 <- !str_detect(words, "[aeiou]")
```

```{r}
# Find all words consisting only of consonants (non-vowels)
no_vowels_2 <- str_detect(words, "^[^aeiou]+$")
identical(no_vowels_1, no_vowels_2)
```

```{r}
words[str_detect(words, "s$")]
```

```{r}
str_subset(words, "s$")
```

```{r}
df <- tibble(
  word = words, 
  i = seq_along(word)
)
df %>% 
  filter(str_detect(word, "x$"))
```

```{r}
x <- c("apple", "banana", "pear")
str_count(x, "a")
```

```{r}
# On average, how many vowels per word?
mean(str_count(words, "[aeiou]"))
```

```{r}
df %>% 
  mutate(
    vowels = str_count(word, "[aeiou]"),
    consonants = str_count(word, "[^aeiou]")
  )
```

```{r}
str_count("lolololol", "lol")
```
```{r}
str_view_all("lolololol", "lol")
```
# 14.4.1.1 Exercises
#For each of the following challenges, try solving it by using both a single regular expression, and a combination of multiple str_detect() calls. Find all words that start or end with x. Find all words that start with a vowel and end with a consonant. Are there any words that contain at least one of each different vowel?
```{r}
words[str_detect(words, "^x|x$")]
start_with_x <- str_detect(words, "^x")
end_with_x <- str_detect(words, "x$")
words[start_with_x | end_with_x]
```

```{r}
str_subset(words, "^[aeiou].*[^aeiou]$") %>% head()
start_with_vowel <- str_detect(words, "^[aeiou]")
end_with_consonant <- str_detect(words, "[^aeiou]$")
words[start_with_vowel & end_with_consonant]
```

```{r}
pattern <-
  cross(rerun(5, c("a", "e", "i", "o", "u")),
    .filter = function(...) {
      x <- as.character(unlist(list(...)))
      length(x) != length(unique(x))
    }
  ) %>%
  map_chr(~str_c(unlist(.x), collapse = ".*")) %>%
  str_c(collapse = "|")
str_subset("aseiouds", pattern)
```

```{r}
str_subset(words, pattern)
```

```{r}
words[str_detect(words, "a") &
  str_detect(words, "e") &
  str_detect(words, "i") &
  str_detect(words, "o") &
  str_detect(words, "u")]
```

# 14.4.2 Extract matches
```{r}
length(sentences)
```

```{r}
head(sentences)
```

```{r}
groceries <- c("rice", "orange", "lettuce", "soup", "blueberries", "chicken")
groceries_match <- str_c(groceries, collapse = "|")
groceries_match
```

```{r}
has_grocery <- str_subset(sentences, groceries_match)
matches <- str_extract(has_grocery, groceries_match)
head(matches)
```

```{r}
has_grocery
```

```{r}
more <- sentences[str_count(sentences, groceries_match) > 1]
str_view_all(more, groceries_match)
```

```{r}
str_extract_all(more, groceries_match)
```

```{r}
str_extract_all(more, groceries_match, simplify = TRUE)
```

```{r}
x <- c("a", "a b", "a b c")
str_extract_all(x, "[a-z]", simplify = TRUE)
```

#14.4.2.1 Exercises
# In the previous example, you might have noticed that the regular expression matched “flickered”, which is not a colour. Modify the regex to fix the problem.

```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")
```

```{r}
colour_match2 <- str_c("\\b(", str_c(colours, collapse = "|"), ")\\b")
colour_match2

more2 <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more2, colour_match2, match = TRUE)

```
# 14.4.3 Grouped matches
```{r}
noun <- "(a|the) ([^ ]+)"

has_noun <- sentences %>%
  str_subset(noun) %>%
  head(10)
has_noun %>% 
  str_extract(noun)
```

```{r}
has_noun %>% 
  str_match(noun)
```

```{r}
tibble(sentence = sentences) %>% 
  tidyr::extract(
    sentence, c("article", "noun"), "(a|the) ([^ ]+)", 
    remove = FALSE
  )
```
#14.4.3.1 Exercises
# Find all words that come after a “number” like “one”, “two”, “three” etc. Pull out both the number and the word.
```{r}
numword <- "\\b(one|two|three|four|five|six|seven|eight|nine|ten) +(\\w+)"
sentences[str_detect(sentences, numword)] %>%
  str_extract(numword)
```
#14.4.4 Replacing matches
#str_replace() and str_replace_all() allow you to replace matches with new strings. The simplest use is to replace a pattern with a fixed string:
```{r}
x <- c("dog", "toucan", "giraffe")
str_replace(x, "[aeiou]", "-")
```

```{r}
str_replace_all(x, "[aeiou]", "-")
```

```{r}
x <- c("1 house", "2 cars", "3 people")
str_replace_all(x, c("1" = "one", "2" = "two", "3" = "three"))
```

```{r}
sentences %>% 
  str_replace("([^ ]+) ([^ ]+) ([^ ]+)", "\\1 \\3 \\2") %>% 
  head(5)
```
# 14.4.4.1 Exercises
#Replace all forward slashes in a string with backslashes.

```{r}
str_replace_all("where/when/why", "/", "\\\\")
```
# 14.4.5 Splitting
# Use str_split() to split a string up into pieces. For example, we could split sentences into words:
```{r}
sentences %>%
  head(5) %>% 
  str_split(" ")
```

```{r}
"a|b|c|d" %>% 
  str_split("\\|") %>% 
  .[[1]]
```

```{r}
sentences %>%
  head(5) %>% 
  str_split(" ", simplify = TRUE)
```

```{r}
fields <- c("Name: Haley", "Country: US", "Age: 5")
fields %>% str_split(": ", n = 2, simplify = TRUE)
```

```{r}
x <- "The quick brown fox jumped over the lazy dog."
str_view_all(x, boundary("word"))
```

```{r}
str_split(x, " ")[[1]]
```

```{r}
str_split(x, boundary("word"))[[1]]
```
#14.4.5.1 Exercises
#Split up a string like “apples, pears, and bananas” into individual components.
```{r}
x <- c("bears, beets, battlestar galatica")
str_split(x, ", +(and +)?")[[1]]
```
# 14.7 stringi
# If you find yourself struggling to do something in stringr, it’s worth taking a look at stringi. The packages work very similarly, so you should be able to translate your stringr knowledge in a natural way. The main difference is the prefix: str_ vs. stri_.